---
title: "NBA Report"
author: "Joey, Eduardo, Shizu, Megan, and Ella"
date: "`r format(Sys.Date(), '%b %d, %Y')`"
output: html_document
---

```{r setup options, include=FALSE, warning=FALSE}

knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE)
```

```{r, establishing the relative filepath}

here::i_am("NBA_Report.Rmd")
```

# Introduction

*Placeholder - fill in with summary of what the report sections will include 



## Section 1 (Eduardo)

Points, assists, and rebounds are the three major statistical categories in basketball. Only three active NBA players have ever led their team in all three categories over the course of a season - LeBron James, Nikola Jokic, and Jayson Tatum.

We decided to tally a combined score (points + assists + rebounds) to identify the 10 players with the highest combined score for the 2025 season, using per-36 minute statistics. 

```{r, combined score table}

library(gt)
readRDS(
  file = here::here("output/Combined_score_table.rds")
)

```
