---
title: "NBA Report"
author: "Joey, Eduardo, Shizu, Megan, and Ella"
date: "`r format(Sys.Date(), '%b %d, %Y')`"
output: html_document
---

```{r setup options, include=FALSE, warning=FALSE}

knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE)
library(ggplot2)
library(gt)
```

```{r, establishing the relative filepath}

here::i_am("NBA_Report.Rmd")
```

# Introduction

*Placeholder - fill in with summary of what the report sections will include, potentially introduce how you can customize the reproducible report



## Section 1 (Eduardo)

Points, assists, and rebounds are the three major statistical categories in basketball. Only three active NBA players have ever led their team in all three categories over the course of a season - LeBron James, Nikola Jokic, and Jayson Tatum.

We decided to tally a combined score (points + assists + rebounds) to identify the 10 players with the highest combined score for the 2025 season, using per-36 minute statistics. 

```{r, combined-score-table}


readRDS(
  file = here::here("output/Combined_score_table.rds")
)

```

## Section 2 (Megan)

Our team also decided to create a scatterplot that shows the association between players' age and their rank in the NBA. The y-axis for this plot was flipped so that the players who are ranked the highest (1, 2, 3) are at the top of the graph, and those that are ranked the lowest (567, 568, 569) are at the bottom.

```{r, scatter-age-rank-mloutti}


#| fig.align = "center",
#| out.width = "600px"
knitr::include_graphics(
  here::here("output/scatter_age_rank_mloutti.png")
)

```

## Section 3 (Ella)

This is our plot on "Yuki Kawamura", "Rui Hachimura", and "James Harden" scores as compared to the league average. 

```{r ella-plot}
#| fig.align = "center",
#| out.width = "600px"
knitr::include_graphics(
  here::here("output/fav_player_ptspread_plot.png")
)
```

## Section 4 (Shizu)

This is our plot on "Yuki Kawamura", "Rui Hachimura", and "James Harden" combined scores in 36 minute intervals.

```{r shizu-plot}
#| fig.align = "center",
#| out.width = "600px"
knitr::include_graphics(
  here::here("output/player_stats_plot_shisomeya.png")
)
```

## Conclusion 

PLACEHOLDER for our discussion on the automated report, how the reproducability of our report can help with future analyses for different groups, etc.